PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-12 qfenv_paper/qf_environment.tex
updated figures and edits

\begin{table} %Subject to significant change based on the classification of environment
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
    $z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
$0.05-0.12$ &Low           &12859                       &14443                           \\
               &High            &18952                       &13387                           \\ 
                              &               &                       &                           \\ \hline
$0.2-0.4$      &Low           &1158                    &3445                           \\
               &High            &817                    &1531                           \\
               &               &                       &                           \\ \hline
$0.4-0.6$      &Low           &1315                       &3390                           \\
               &High            &848                       &1499                           \\
               &               &                       &                           \\ \hline
$0.6-0.8$      &Low           &1158                       &2303                           \\
               &High            &900                       &1275                           \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \bigskip 
    {\bf Notes}: Number of galaxies in the mass complete subsamples derived in Section \ref{sec:sample}. The subsamples are classified based on environment and star formation rate. The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. 
  \end{center}
\end{table}

@@

In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes. Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a preliminary correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio. This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}. However, the effect of the mass correction was negligible for the quiescent fraction evolution results. As a result, we do not discuss the issues with photometric measurements any further in this paper. The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_histogram.png,height=0.5\textwidth}
     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution of the distribution from quiescent galaxies is colored in red. Each redshift panel is divided into three sections of by the environment classification threshold (vertical black lines): low density environment $n_{\rm{env}} < 1.5$ and high density environment $n_{\rm{env}} > 3.5$. The percentages of the redshift bin contained in the environment classifications are presented above the distribution. For example at $0.2 < z < 0.4$, $56.0 \%$ of galaxies in the redshift bin have low density environments while $29.0\%$ of galaxies in the redshift bin have high density environments. }      \label{fig:envcount}
    \end{center}
\end{figure*}

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.

\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$. The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text. Darker shading indicates lower redshift.}         \label{fig:qf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \label{sec:qfevol}). More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EVOLUTION OF THE QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments. As in Figure \ref{fig:smf}, the darker shading represent lower redshift bins. The width of the quiescent fraction represents the uncertainty from sample variance. As done in Section \ref{sec:smfevol} for the stellar mass function, we use the standard jack-knife technique

Most noticeably in Figure \ref{fig:qf}, $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment. In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation. With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{blanton09a}).

@@

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$). At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}. \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment. Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which also agree with our low density environment $f_{\rm{Q}}$.

For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment. The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments. Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR. $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$. Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference evenly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.

Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \label{sec:env_qf_evol}. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} 
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.

>>>>

\begin{table} %Subject to significant change based on the classification of environment
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
    $z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
$0.05-0.12$ &Low           &12859                       &14443                           \\
               &High            &18952                       &13387                           \\ 
                              &               &                       &                           \\ \hline
$0.2-0.4$      &Low           &1158                    &3445                           \\
               &High            &817                    &1531                           \\
               &               &                       &                           \\ \hline
$0.4-0.6$      &Low           &1315                       &3390                           \\
               &High            &848                       &1499                           \\
               &               &                       &                           \\ \hline
$0.6-0.8$      &Low           &1158                       &2303                           \\
               &High            &900                       &1275                           \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Number of galaxies in the mass complete subsamples derived in Section \ref{sec:sample}. The subsamples are classified based on environment $n_{\rm{env}}$ and star formation rate (star-forming or quiescent). The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. 
    \bigskip
\end{table}

@@

In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes. Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a preliminary correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio. This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}. However, the effect of the mass correction was negligible for the quiescent fraction evolution results. As a result, we do not discuss the issues with photometric measurements any further in this paper. The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_edgecut_histogram.png,height=0.5\textwidth}
     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Each redshift panel is divided into three sections of by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 1.5$ and high density environment $n_{\rm{env}} > 3.5$. The percentages of the redshift bin contained in the environment classifications are presented above the distribution. For example at $0.2 < z < 0.4$, $56.0 \%$ of galaxies in the redshift bin have low density environments while $29.0\%$ of galaxies in the redshift bin have high density environments. }      \label{fig:envcount}
    \end{center}
\end{figure*}

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$. The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text. Darker shading indicates lower redshift.}         \label{fig:qf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction.

With the suffic ient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}). More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EVOLUTION OF THE QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments. As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading: darker with lower redshift. In order to calculate the uncertainty for the quiescent fraction, we follow the same steps in the standard jackknife technique as we did for the SMF in Section \ref{sec:smfcalc}. We represent the quiescent fraction uncertainty by the width in Figure \ref{fig:qf}.

Most noticeably in Figure \ref{fig:qf}, we find $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment. In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation. With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{blanton09a}).

@@

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements for analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment for SDSS galaxies. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$).

At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}. \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment. Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \cite{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.

For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment. The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments. Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR. $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$. Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.

Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \ref{sec:env_qf_evol}. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} \label{eq:qffit}
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.
